Self Regulation Ontology Retest Analyses

### 2018-05-07 code/SRO_Retest_Analyses.Rmd
building new report
created new report

@@

## Transformation effects

All results reported above were for non-transformed dependent variables.

We could compare the reliability (point) estimates for meaningful variables that have been transformed in the full dataset and transformed the same way in the retest dataset as well.

```{r}
test_data_tmp <- test_data
retest_data_tmp <- retest_data

test_data <- read.csv(paste0(retest_data_path,'t1_data/meaningful_variables_clean.csv'))
test_data$X <- as.character(test_data$X)
names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
retest_data <- read.csv(paste0(retest_data_path,'meaningful_variables_clean.csv'))
retest_data$X <- as.character(retest_data$X)
names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
```

```{r}
numeric_cols_mngfl = c()

for(i in 1:length(names(test_data))){
  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
    numeric_cols_mngfl <- c(numeric_cols_mngfl, names(test_data)[i])
  }
}

rel_df_mngfl <- data.frame(icc = rep(NA, length(numeric_cols_mngfl)))

row.names(rel_df_mngfl) <- numeric_cols_mngfl

for(i in 1:length(numeric_cols_mngfl)){
  rel_df_mngfl[numeric_cols_mngfl[i], 'icc'] <- get_icc(numeric_cols_mngfl[i])
}

rel_df_mngfl$dv = row.names(rel_df_mngfl)
row.names(rel_df_mngfl) = seq(1:nrow(rel_df_mngfl))
rel_df_mngfl$task = 'task'
rel_df_mngfl[grep('survey', rel_df_mngfl$dv), 'task'] = 'survey'
rel_df_mngfl[grep('holt', rel_df_mngfl$dv), 'task'] = "task"
rel_df_mngfl
```

```{r warning=FALSE, message=FALSE}
ggplotly(rel_df_mngfl %>%
  filter(grepl("logTr", dv)) %>%
  mutate(dv = gsub(".ReflogTr", "", dv),
         dv = gsub(".logTr", "", dv)) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv") %>%
  ggplot(aes(icc.x, icc.y, color=task, label=dv))+
  geom_point()+
  theme_bw()+
  xlab("Reliability for transformed variable")+
  ylab("Reliability for raw variable")+
  geom_abline(slope=1, intercept=0),
  label=dv)
```

>>>>

```{r}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
```

@@
